Computation and comparison of the stable Northeastern US marine boundary layer

### 2020-12-01 Paper/results.tex

%%%%%%%%%%%%%%% GRID STUDY: INTEGRAL LENGTH %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[h!]
\caption{\label{tab:GridStudyLscale} The calculated turbulent integral
  lengthscale for each of the grid resolutions} \centering
\begin{tabular}{ccccc}
  \hline
  Case              & dx [m] & Longitudinal L  & Lateral L \\
  \hline
  Nalu-wind coarse  &  10.0  & 36.43 m         & 0.0 m     \\
  Nalu-wind medium  &   5.0  & 21.49 m         & 4.52 m    \\
  Nalu-wind fine    &   2.5  & 25.25 m         & 5.92 m    \\
% AMR-wind fine     &   2.5  & 27.689340 m     & 9.332672   \\
\hline
\end{tabular}
\end{table}

@@

\subsubsection{Wind spectra and turbulent correlation}

@@

A comparison of the averaged $\langle R_{11}(\boldsymbol{\xi})\rangle$
correlation coefficient is shown in figure
\ref{fig:CompareAMRvsNaluRij}.

@@

%%%%%%%%%%% Compare Nalu/AMR lengthscale %%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Postprocessing/ABLLength/CompareAMRNalu_ABL_Lengthscales.ipynb
\begin{figure} %[hbt!]
  \centering
  \fxnote{UPDATE THIS FIGURE}\\
  \includegraphics[width=2.5in]{figures/Compare_AMRWind_NaluWind/AMRWind_NaluWind_Lengthscale_Stable_z20_Longitudinal.png}
  \includegraphics[width=2.5in]{figures/Compare_AMRWind_NaluWind/AMRWind_NaluWind_Lengthscale_Stable_z20_Lateral.png}

  \caption{\label{fig:CompareAMRvsNaluRij}
    Comparison of AMR-Wind and Nalu-Wind $\langle R_{11}
    \rangle$ correlation at z=20m. }
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\subsubsection{ABL integrated quantities}
Describe integrated quantities

%%%%%%%%%%%%%%% Compare AMR integrated quantities, all WS %%%%%%%%%%%%%%
% See Postprocessing/ABLStats/AMRWind_NaluWind_stable_AllWS_2p5Cubed.ipynb
\begin{table}
\caption{\label{tab:CompareAMRallWS} Comparison of Stable ABL for all
  wind speeds} \centering
\begin{tabular}{cccccc}
  \hline
  Code & Wind speed & TI      &  $\alpha$  &   $u_\tau$  &  Obukhov  L \\
  \hline
  AMRWind & 5m/s      & 0.048255 &  0.165552 &  0.157399  & 52.512434 \\
  AMRWind & 10m/s     & 0.050580 &  0.160337 &  0.318941  &  57.233491 \\
  AMRWind & 15m/s     & 0.055034 &  0.118190 &  0.510645  & 131.341634 \\
  \hline
\end{tabular}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection{Horizontally averaged profiles}

%%%%%%%%%%% stable WS profiles %%%%%%%%%%%%%%%%%%%%%%%%%
% Created in Postprocessing/ABLStats/AMRWind_NaluWind_stable_AllWS_2p5Cubed.ipynb
\begin{figure}[hbt!]
  \label{fig:CompareAMRallWS}
  \centering
  \includegraphics[width=2.5in]{figures/AMRWind_allWS/AMRWind_stable_WS.png}
  \includegraphics[width=2.5in]{figures/AMRWind_allWS/AMRWind_stable_WDir.png}
  \caption{Calculation of the wind spectra $S_i$ for LES of stable
    5m/s, 10m/s, and 15m/s cases at z=20m, 40m, and 60m.  The black
    vertical lines correspond to the maximum resolvable frequency
    $f_{max}$ according to equation (\ref{eq:fmax}). }
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%%%%%%%%%%%%%%% GRID STUDY: INTEGRAL LENGTH %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table} %[h!]
\caption{\label{tab:GridStudyLscale} The calculated turbulent integral
  lengthscale for each of the grid resolutions} \centering
\begin{tabular}{ccccc}
  \hline
  Case              & dx [m] & Longitudinal L  & Lateral L \\
  \hline
  Nalu-wind coarse  &  10.0  & 36.4 m         & 0.0 m     \\
  Nalu-wind medium  &   5.0  & 21.5 m         & 4.52 m    \\
  Nalu-wind fine    &   2.5  & 25.3 m         & 5.92 m    \\
\hline
\end{tabular}
\end{table}

@@

@@

@@

%% A comparison of the averaged $\langle R_{11}(\boldsymbol{\xi})\rangle$
%% correlation coefficient is shown in figure \ref{fig:CompareAMRvsNaluRij}.

%% %%%%%%%%%%% Compare Nalu/AMR lengthscale %%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% % Postprocessing/ABLLength/CompareAMRNalu_ABL_Lengthscales.ipynb
%% \begin{figure} %[hbt!]
%%   \centering
%%   \fxnote{UPDATE THIS FIGURE}\\
%%   \includegraphics[width=2.5in]{figures/Compare_AMRWind_NaluWind/AMRWind_NaluWind_Lengthscale_Stable_z20_Longitudinal.png}
%%   \includegraphics[width=2.5in]{figures/Compare_AMRWind_NaluWind/AMRWind_NaluWind_Lengthscale_Stable_z20_Lateral.png}

%%   \caption{\label{fig:CompareAMRvsNaluRij}
%%     Comparison of AMR-Wind and Nalu-Wind $\langle R_{11}
%%     \rangle$ correlation at z=20m. }
%% \end{figure}
%% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Using the results of the stable cases described in \ref{sec:CFDsetup},
as well as the computations from the previous study in
\cite{cheung2020large}, we can examine the influence of wind speed and
stratification on offshore ABL behavior.  In this section we first
compare the differences between the three stable ABL cases, and then
compare their behavior with the previously computed neutral and
unstable counterparts.

\subsubsection{ABL integrated quantities}
From the AMR-Wind calculations of the stable ABL at 5m/s, 10m/s, and
15m/s, a number of quantities can be computed to compare with the
measured targets from Archer et al \cite{archer2016predominance}.

The Obukhov length $L_{Ob}$ can be calculated as
\begin{equation}
  L_{Ob} = -\frac{u_\tau^3 T_0}{\kappa g \langle \overline{w'T'} \rangle}
\end{equation}
where the $\kappa$=0.41 is the Kolmogorov constant, $g$ is the
gravitational acceleration, and $\langle \overline{w'T'} \rangle$ is the
horizontally and time-averaged temperature flux.  In this study we use
the same classification guidelines as Archer et al
\cite{archer2016predominance}, and identify cases where $100 < L_{Ob}
< 500$ as ``stable'', and cases where $5 < L_{Ob}<100$ as ``very stable''.

%%%%%%%%%%%%%%% Compare AMR integrated quantities, all WS %%%%%%%%%%%%%%
% See Postprocessing/ABLStats/AMRWind_NaluWind_stable_AllWS_2p5Cubed.ipynb
\begin{table}
\caption{\label{tab:CompareAMRallWS} Comparison of Stable ABL for all
  wind speeds} \centering
\begin{tabular}{ccccccc}
  \hline
  Code & Wind speed & TI      &  $\alpha$  &   $u_\tau$  &  Obukhov  $L_{Ob}$ & Stability \\
  \hline
  AMRWind & 5m/s      & 0.0483 &  0.166 &  0.157 m/s  &  52.5 m   & Very stable\\
  AMRWind & 10m/s     & 0.0506 &  0.160 &  0.319 m/s  &  57.2 m   & Very stable\\
  AMRWind & 15m/s     & 0.0550 &  0.118 &  0.511 m/s  & 131.3 m   & Stable \\
  \hline
\end{tabular}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection{Flow behavior and horizontally averaged profiles}

%%%%%%%%%%% z=20m snapshot pics %%%%%%%%%%%%%%%%%%%%%%%%%
% Created in Postprocessing/ABLStats/AMRWind_NaluWind_stable_AllWS_2p5Cubed.ipynb
\begin{figure}[hbt!]
  \centering
  \includegraphics[width=2.5in]{figures/snapshots/05ms/velh_mag_z20.png}
  \includegraphics[width=2.5in]{figures/snapshots/05ms/velz_z20.png} \\

  \includegraphics[width=2.5in]{figures/snapshots/10ms/velh_mag_z20.png}
  \includegraphics[width=2.5in]{figures/snapshots/10ms/velz_z20.png} \\

  \includegraphics[width=2.5in]{figures/snapshots/15ms/velh_mag_z20.png}
  \includegraphics[width=2.5in]{figures/snapshots/15ms/velz_z20.png} \\
  \caption{ \label{fig:SnapshotsZ20} Snapshots of the horizontal
    velocity and vertical velocity }
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%% side snapshot pics %%%%%%%%%%%%%%%%%%%%%%%%%
% Created in Postprocessing/ABLStats/AMRWind_NaluWind_stable_AllWS_2p5Cubed.ipynb
\begin{figure}[hbt!]
  \centering
  \includegraphics[height=2.0in]{figures/snapshots/05ms/velh_mag_side.png} \\

  \includegraphics[height=2.0in]{figures/snapshots/10ms/velh_mag_side.png} \\

  \includegraphics[height=2.0in]{figures/snapshots/15ms/velh_mag_side.png} \\

  \caption{ \label{fig:SnapshotsSide} Snapshots of the horizontal
    velocity and vertical velocity }
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%% stable WS profiles %%%%%%%%%%%%%%%%%%%%%%%%%
% Created in Postprocessing/ABLStats/AMRWind_NaluWind_stable_AllWS_2p5Cubed.ipynb
\begin{figure}[hbt!]
  \label{fig:CompareAMRallWS}
  \centering
  \includegraphics[width=2.5in]{figures/AMRWind_allWS/AMRWind_stable_WS.png}
  \includegraphics[width=2.5in]{figures/AMRWind_allWS/AMRWind_stable_WDir.png}
  \caption{Comparison of the horizontal wind speed and wind direction
    profile for the stable 5m/s, 10m/s, and 15m/s boundary layers. }
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%% stable WS profiles %%%%%%%%%%%%%%%%%%%%%%%%%
% Created in Postprocessing/ABLStats/AMRWind_NaluWind_stable_AllWS_2p5Cubed.ipynb
\begin{figure}[hbt!]
  \label{fig:CompareAMRallTTI}
  \centering
  \includegraphics[width=2.5in]{figures/AMRWind_allWS/AMRWind_stable_TI.png}
  \includegraphics[width=2.5in]{figures/AMRWind_allWS/AMRWind_stable_T.png}
  \caption{Comparison of the turbulence intensity and temperature
    profile for the stable 5m/s, 10m/s, and 15m/s boundary layers. }
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
